%-------------------------------------------------------------------
% Main CV document
%-------------------------------------------------------------------

\documentclass[letterpaper,10pt]{article}

% Load custom style file
\usepackage{cv-style}


% Begin document
\begin{document}


% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} R @{}}
\textcolor{titlecolor}{\namefont{conor wood hayes}} \\[4pt]
\href{https://github.com/cwoodhayes}{\raisebox{-0.05\height}\faGithub\ cwoodhayes} \ $|$ \ 
\href{https://linkedin.com/in/cwoodhayes}{\raisebox{-0.05\height}\faLinkedin\ cwoodhayes} \ $|$ \ 
\href{mailto:cwoodhayes@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ cwoodhayes@gmail.com} \ $|$ \ 
Chicago, IL \\
\end{tabularx}
\vspace{-17pt}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}
% FIELD ROBOTICS SUMMARY
Hands-on robotics and embedded systems engineer with extensive experience building \& deploying
real-world hardware, autonomy stacks, and mission-critical embedded systems end-to-end.
Background includes avionics for rockets \& spacecraft, PCBA and embedded firmware for medical wearables,
and ROS2 perception \& manipulation systems.
% and cloud architecture \& development for IoT. 
Strong focus on practical robotics, field testing, and reliability in harsh environments.

% RESEARCH ROBOTICS SUMMARY
% TODO

% FORWARD DEP ENGINEER SUMMARY
% TODO

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}X@{}}
\textbf{Firmware/PCBA:} Microcontroller development (ARM Cortex-M, NRF5x, Raspberry Pi), bare-metal
development, PCB design (Altium), PCB bring-up \& debug (logic analyzer, oscilloscope), BLE, SPI, I2C, CAN, RS-485, NOR/NAND Flash\\
\textbf{Control:} inverse/forward kinematics, rigid body dynamics, PID, impedance control, joint encoders \\
\textbf{Perception:} SLAM, state estimation, EKF, particle filter, IMUs, GPS, magnetometer/barometer, depth cameras \\
\textbf{Planning: } Path planning (A*, D*, RRT), MoveIt, OMPL, embodied foundation models \\
\textbf{Simulation:} Gazebo, RViz, CoppeliaSim (V-REP) \\
\textbf{Software:} ROS2, Linux, Git, Docker, CI/CD (GitHub Actions, Jenkins, AWS CodePipeline), AWS, API design \\
\textbf{AI/ML:} pytorch, OpenCV, NumPy, Pandas, Matplotlib, Seaborn, SciPy, scikit-learn, Sympy, Neural Networks, SVM \\
\textbf{Languages:} Python, C, C++, CMake, Makefile, Rust, SQL, TypeScript, Bash/Zsh, Verilog, Assembly, linker scripts \\
\textbf{Systems Engineering:} Agile development, JIRA, Failure analysis, Reliability Engineering, QA frameworks
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{education}{Northwestern University}{M.S. Robotics}{2025--Aug 2026 (expected)}
Focus on perception, manipulation, and embodied AI. Selected Coursework:
\begin{multicols}{2}
\begin{itemize}[leftmargin=*, itemsep=0pt, parsep=0pt, topsep=0pt]
\item Robotic Manipulation (Kevin Lynch)
\item AI \& Machine Learning for Robotics (Brenna Argall)
\item Reasoning \& Planning in the Foundation Model Era (Li Manling)
\item Sensing, Navigation, \& ML for Robotics (Matthew Elwin)
\end{itemize}
\end{multicols}


\end{education}
\begin{education}{University of Southern California}{B.S. Computer Engineering \& Computer Science}{2015-2019}
    % GPA: 3.82, 
    Magna Cum Laude. Minor in Chinese for the Professions, Thematic Option (Honors in Liberal Arts)
\end{education}

%----------------------------------------------------------------------------------------
%	PROJECTS 
%----------------------------------------------------------------------------------------
\section{Projects}
\begin{joblong}{Northwestern University}{PenPal -- Franka Panda 7DoF Manipulation System}{Nov-Dec 2025}
    \item Developed perception -> planning -> control pipeline in ROS2 for real-time handwriting on arbitrarily-oriented moving surface.
    \item Implemented camera calibration, pose estimation, online trajectory generation, and closed-loop visual cartesian control.
    \item Tuned controllers, handled noise, delays, and system constraints to ensure consistent physical performance.
\end{joblong}

\begin{joblong}{USC Rocket Propulsion Lab}{\href{https://cwhayes.squarespace.com/tech/rpl-tiv}{Traveler IV} - First 100\% undergrad-made rocket to fly to space}{2015-2019}
    \item Built \& led 30-person engineering team. Oversaw all software (C++), hardware (Altium), and EGSE for multiple iterations of custom avionics system, which successfully flew to, survived, and returned from space.
    \item Designed, tested, and hand-assembled avionics boards robust enough to operate in desert + space + high-G environments.
    \item Led analysis effort to determine flight path, published \href{https://static1.squarespace.com/static/549ce89be4b0cddb26c4894b/t/5ce58210e4966b7fc63fbe10/1558544951210/Traveler-IV-Whitepaper}{Traveler IV Whitepaper} concluding the rocket crossed the Karman Line.
    \item Co-designed launch procedures coordinating 100+ engineers in remote desert environment, resulting in a successful launch.
    \item Debugged electrical, software, and radio issues in the field under timing constraints, inclement weather, and poor infrastructure.
    \item Wrote still-in-use \href{https://github.com/cwoodhayes/FlashLog-archive}{software} providing fault+radiation-tolerant telemetry storage on a NOR flash memory chip.
    \item Kicked off lab-wide cultural reform after handling an internal harassment case to help the lab be a safer space for young engineers.
\end{joblong}
\begin{joblong}{Northwestern University}{Algorithms from Scratch - ML algorithms implemented without ML libraries in Python}{April 2025}
    \item Implemented particle filter, developed measurement+control model, and applied to \href{http://asrl.utias.utoronto.ca/datasets/mrclam/index.html}{MRCLAM} dataset for robot localization.
    \item Implemented online A* planning + trajectory control to navigate simulated diff-drive robot around an arena.
    \item Proposed, implemented, and trained 97\% accurate SVM-based algorithm for landmark visibility prediction on MRCLAM dataset.
\end{joblong}
\vspace{-1em}
\begin{joblong}{CHSC + UCLA}{AustereChain - Blockchain-Based Resource Management for Autonomous Systems in Austerity}{April 2025}
    \item Proposed blockchain-based framework to enable decentralized resource negotiation for autonomous systems in low-resource environments (i.e. space stations),
    to be submitted to IEEE-SMC-IT 2026.
\end{joblong}
\begin{joblong}{CHSC + UCLA}{MIDI Glove - Wearable Accelerometer-Based Human Pose Detection}{April-May 2025}
    \item Researched methodologies for ML-based human pose estimation to create a low-cost MIDI instrument controller.
    \item Created initial hardware prototype of arm+hand pose-estimator glove.
\end{joblong}
\begin{joblong}{Independent}{Rust \href{https://github.com/cwoodhayes/letterboxed_solver}{Letterboxd Solver}}{April 2025}
    \item Designed \& implemented A*-based algorithm in Rust to optimally solve \textit{New York Times} letterboxd puzzles.
    \item Optimized runtime down to <1ms for NYT puzzles; extended to arbitrary puzzle size+geometry.
\end{joblong}

% \begin{joblong}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

\begin{joblong}{Conor Hayes Software Consulting (CHSC)}{Independent Consultant}{2023 - 2025, IN/NY/CA}
\item Provided architecture guidance and hands-on implementation for a reusable hardware testing framework (Python) and 
its application to two \$500K high-speed test racks (SMU, PSU, PDU, Pickering simulators; CAN, USB, ethernet, GPIB, SCPI) for space \& nuclear fusion projects, 
driving successful on-time delivery after 8mos.
\item Designed high-level control software, database, and cloud architecture for a digital-twinned battery test system (Python, SQL, AWS); assisted 8-person team
to develop, ship, \& deploy the system to the assembly line of a \$22B satellite firm.
\item Redesigned BLE protocol (C, TypeScript) for NRF52-based wearable. +2 sensors, +800\% bandwidth, -10\% power consumption.
\item Provided initial computer vision support for autonomous refueling robot for self-driving electric vehicles.
\item Set up CI/CD pipelines using AWS+GitHub Actions for backend of an IoT startup, completely automating a previously 3-hour manual deployment process.
\item Prototyped a low-latency peer-to-peer telepresence platform for controlling robots via web client (WebRTC, AWS, TypeScript)
\item Created \href{https://cwhayes.squarespace.com/tech/chsc}{Deep Tech Product Management slide deck} to introduce research-oriented 
tech startups to product design \& development best practices.
\item Built self-sustaining consulting business as solo entrepreneur; sourced clients, negotiated contracts, ran S-Corp.
\end{joblong}%

% not sure why i need this but if i dont have it theres a mysterious space here
% \vspace{-1em}
\begin{joblong}{Wesper, Inc}{Software Engineer (8th employee @ startup)}{2020 - 2022, New York City}
\item Owned firmware development (C, NRF5X) to support multiple hardware iterations of a sleep apnea diagnosis wearable, from late-stage prototypes to FDA-approved, mass-produced revenue-generating product.
\item Integrated new sensors, developed on-device algorithms, and expanded BLE interface to enable low-power real-time reporting of patient heart rate, blood oxygen level, and sleep posture.
\item Developed hardware-in-the-loop simulation infrastructure (C, Python) over JTAG to enable algorithm development in firmware.
\item Created automated board programming+testing software used to mass-produce the product in China.
\item Improved supply chain resilience by enabling firmware to target multiple MCU's (C, Makefile, linker scripts).
\item Led a team of 3 to build backend from scratch (AWS ECS, EC2, $\lambda$, S3, RDS MySQL, Python) to ingest and process all patient data.
\item Served as devops engineer for the company; owned responsibility for all backend deployments.
\item Worked directly with CTO, VP of Engineering, and Director of Algorithms, supporting growth from 8 -> 23 employees, 0 -> 1000+ patients per month
\item Worked with iOS team to funnel real-time logging from the firmware, iPhone app, and backend into a single logging aggregator (logz), enabling end-to-end traceability for live support.
\end{joblong}

\begin{joblong}{Honeybee Robotics}{Software \& Electrical Engineering Intern}{May - Aug 2018, Pasadena, CA}
\item Developed drivers, middleware (C++, ZeroMQ), GUIs (Qt), and PCB's (Altium) for robotic assemblies for extreme environments (Mars, Venus, Europa, Arctic circle)
\item Worked directly with project teams of mechanical, electrical, and systems engineers to spec \& implement new features in 
an internal ROS-like testing framework, with 200+ source files and 100,000+ lines of C++ code.
\item Designed, tested, and validated PCB to provide human-in-the-loop control of small drills on remote oil rigs.
\item Wrote python data processing library on own initiative to save up to 10min/experiment, adopted by 50+ mechanical engineers across company.
\end{joblong}

\begin{joblong}{NASA Jet Propulsion Laboratory}{Flight Electronics Intern (Group 349E)}{Jan - Aug 2017, Pasadena, CA}
\item Developed the automated hardware and software test suite (C, Python, SPARC Assembly) for the first deep-space-capable cubesat C\&DH board (Sphinx). 
\item Supported initial board bring-up, discovered \& documented critical bugs in novel rad-hardened NAND flash controller and other peripherals.
\item Credited inventor on NASA Copyright of Invention NPO 51462-CP for the above.
\end{joblong}

%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------
\vspace{-1.0em}  % reduce vertical gap
\section{Awards}
\award{American Institute of Astronautics and Aeronautics}{Achievement Award}{Oct 2019}
\award{National Academy of Engineering/USC}{Grand Challenges Scholar}{May 2019}
\award{University of Southern California}{Renaissance Scholar (0.9\% of graduating class)}{May 2019}
\award{University of Southern California}{Trustee Scholar (4-year, 1/2 tuition merit scholarship)}{Apr 2015}

% \vfill
% \center{\footnotesize Last updated: \today}

%----------------------------------------------------------------------------------------
%	HOBBIES
%----------------------------------------------------------------------------------------
\section{Hobbies}
\begin{tabularx}{\linewidth}{@{}X@{}}
\textbf{Recorded Music:} Accumulated 700,000+ Spotify streams on original music under 
artist name \textit{\href{https://open.spotify.com/artist/13DmASWA762GpdaSAAR90l}{Wise John}} (39 songs, 2 albums, 1 EP). \\
\textbf{Live Music:} Sold 170 tickets across bill at NYC's Mercury Lounge (2024). Performed 20+ live shows in NYC, LA, and elsewhere. \\
\textbf{Travel \& Sports:} backpacking (wilderness \& urban), swimming, basketball, tennis. \\
\textbf{Languages:} English (native), Mandarin Chinese (conversational)
\end{tabularx}

\end{document}
